Data Management for LSST Special Programs

### 2024-03-27 sec_sci.tex
group user-related info
active section headings

\section{Recommendations to Enable Science from Special Programs}\label{sec:sci}

@@

\subsection{Region and Observing Mode Labels}\label{ssec:sci_labels}

@@

\textbf{Region Labels -- } 
Applied to a visit based on its Right Acension and Declination.

@@

\textbf{Observing Mode Labels -- } 
Applied to a visit based on the scheduler mode at the time of the observation
(i.e., survey cadence or strategy).

@@

\subsection{Special Processing}\label{ssec:sci_sproc}

@@

\subsection{Prompt Processing}\label{ssec:sci_pproc}

@@

\subsection{Computational Resources for User-Generated Processing}\label{ssec:sci_comp}

@@

\subsection{Rubin Science Platform Capabilities}\label{ssec:sci_rsp}

>>>>

\section{Recommendations for Rubin DM to Enable Science from Special Programs}\label{sec:sci}

@@

\subsection{Apply Region and Observing Mode Labels}\label{ssec:sci_labels}

@@

\textbf{Region labels -- } 
applied to a visit based on its Right Acension and Declination.

@@

\textbf{Observing mode labels -- } 
applied to a visit based on the scheduler mode at the time of the observation
(i.e., survey cadence or strategy).

@@

\subsection{Run Special Processing When Possible and Necessary}\label{ssec:sci_sproc}

@@

\subsection{Include Special Programs Data in Prompt Processing}\label{ssec:sci_pproc}

@@

\subsection{Provide Computational Resources for User-Generated Processing}\label{ssec:sci_comp}

@@

\subsubsection{Rubin Science Platform Capabilities}\label{sssec:sci_rsp}
